The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-05 outputs/paper/paper.Rmd
Result session edited

To sum up, all of variables pointed same thing: need for more healthcare system in 1987 Thailand, or unbalance of healthcare system between regions, communities, cities, and religion. Furthermore, from some variables such as education level, we could find that some specific groups would not believe healthcare system 100%.

>>>>

To sum up, all of variables pointed same direction: need for better healthcare system in 1987 Thailand, or unbalance of healthcare system between regions, communities, cities, and religion. Moreover, from some variables such as education level, we could find that some specific groups did not trust the healthcare system 100%. Combining all weakness in healthcare system in Thailand, it presents unexpected result from contemporary thought, which is immunization status was inclined to mother more than healthcare facilities.
